Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-04-01 doc/paper.Rmd
un-gitingore paper.docx for emilio

This study adds to the growing body of work that finds delayed effects of climate drivers on vital rates without *a priori* assumptions about the influence of particular climate windows [@tenhumbergTimelaggedEffectsWeather2018; @tellerLinkingDemographyDrivers2016; @eversLaggedDormantSeason2021].
We found evidence for delayed effects of drought which are sometimes stronger predictors of vital rates than more recent conditions.
The approach we took offers an unbiased way of identifying these delayed effects without overfitting (but see @pierreCriticalWindowsMethod2020 and @ogleQuantifyingEcologicalMemory2015a for alternative methods), yet few demographic studies have the data required for modeling lagged effects [@tellerLinkingDemographyDrivers2016; @croneHowPlantEcologists2011].
This demonstrates the importance of long term demographic experiments in determining the effects of changing habitats on populations.

@@

-   Address how all but the smallest sizes are shrinking on average over the period of this study <!--# this is not true.  A bug previously made it look like all plants were shrinking.  Keeping this because citations -->(Figure \@ref(fig:growth-size)).
    Cite: @brunaExperimentalAssessmentHeliconia2002; Begg 1980; Wright 1996; Rundel et al. 1998.

>>>>

This study adds to the growing body of work that finds delayed effects of climate drivers on vital rates without *a priori* assumptions about the influence of particular climate windows [@tenhumbergTimelaggedEffectsWeather2018; @tellerLinkingDemographyDrivers2016; @eversLaggedDormantSeason2021]. We found evidence for delayed effects of drought which are sometimes stronger predictors of vital rates than more recent conditions. The approach we took offers an unbiased way of identifying these delayed effects without overfitting (but see @pierreCriticalWindowsMethod2020 and @ogleQuantifyingEcologicalMemory2015a for alternative methods), yet few demographic studies have the data required for modeling lagged effects [@tellerLinkingDemographyDrivers2016; @croneHowPlantEcologists2011].
This demonstrates the importance of long term demographic experiments in determining the effects of changing habitats on populations.
<!--# Or something like "some of these long-term studies exist and are prime for doing these kinds of analyses" -->

@@
